My wonderful paper

### 2024-12-06 _manuscript/_tex/index.tex
change document class

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{jds}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My wonderful paper},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My wonderful paper}
\author{}
\date{}

\begin{document}
\maketitle
\begin{abstract}
Unexpected results in data analysis can prompt researchers to examine
data quality and analysis steps. While some researchers can typically
diagnose issues effectively with a few checks, others may struggle to
identify appropriate checks to diagnose the problem. {[}an example of
check{]} These checks are often informal and difficult to trace and
discuss in publications, resulting in others questioning the
trustworthiness of the analysis. To address this, we formalize the
informal checks into an \emph{analysis plan} that encompasses the
analysis steps and (the unit tests): one test for whether the result
meets expectations and multiple tests for checking the analysis. We then
present a procedure to assess the quality of these unit tests based on
their accuracy and redundancy on simulated versions of the original
data. The accuracy is assessed using binary classification metrics,
\emph{i.e.}, precision and recall, while redundancy is calculated using
mutual information. This procedure can be used to conduct a sensitivity
analysis, compare different analysis plans, and to identify the optimal
cutoff point for the unit tests.
\end{abstract}

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

README:

\begin{itemize}
\tightlist
\item
  \emph{Check for TODOs}
\item
  Literature review: Section \emph{diagnosing unexpected outcomes in
  data analysis}
\item
  \emph{Discussion} and \emph{Conclusion}
\item
  In Section \emph{Application}: provide more context on the
  PM10-mortality study and add reference of the {[}0, 0.005{]} PM10
  coefficient
\item
  Roger's Orcid???
\end{itemize}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
]{interact}

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{orcidlink}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My wonderful paper},
  pdfauthor={H. Sherry Zhang; Roger D. Peng},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My wonderful paper}
\author{H. Sherry Zhang$\textsuperscript{1}$, Roger D.
Peng$\textsuperscript{1}$}

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@austin.utexas.edu}{\nolinkurl{huize.zhang@austin.utexas.edu}}. Roger
D.
Peng. Email: \href{mailto:roger.peng@austin.utexas.edu}{\nolinkurl{roger.peng@austin.utexas.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1}  University of Texas at Austin,  
\begin{abstract}
Unexpected results in data analysis can prompt researchers to examine
data quality and analysis steps. While some researchers can typically
diagnose issues effectively with a few checks, others may struggle to
identify appropriate checks to diagnose the problem. {[}an example of
check{]} These checks are often informal and difficult to trace and
discuss in publications, resulting in others questioning the
trustworthiness of the analysis. To address this, we formalize the
informal checks into an \emph{analysis plan} that encompasses the
analysis steps and (the unit tests): one test for whether the result
meets expectations and multiple tests for checking the analysis. We then
present a procedure to assess the quality of these unit tests based on
their accuracy and redundancy on simulated versions of the original
data. The accuracy is assessed using binary classification metrics,
\emph{i.e.}, precision and recall, while redundancy is calculated using
mutual information. This procedure can be used to conduct a sensitivity
analysis, compare different analysis plans, and to identify the optimal
cutoff point for the unit tests.
\end{abstract}

\setstretch{2}
README:

\begin{itemize}
\tightlist
\item
  \emph{Check for TODOs}
\item
  Literature review: Section \emph{diagnosing unexpected outcomes in
  data analysis}
\item
  \emph{Discussion} and \emph{Conclusion}
\item
  In Section \emph{Application}: provide more context on the
  PM10-mortality study and add reference of the {[}0, 0.005{]} PM10
  coefficient
\end{itemize}

### 2024-12-06 index.qmd
change document class

---
title: "My wonderful paper"
abstract: "Unexpected results in data analysis can prompt researchers to examine data quality and analysis steps. While some researchers can typically diagnose issues effectively with a few checks, others may struggle to identify appropriate checks to diagnose the problem. [an example of check] These checks are often informal and difficult to trace and discuss in publications, resulting in others questioning the trustworthiness of the analysis. To address this, we formalize the informal checks into an *analysis plan* that encompasses the analysis steps and (the unit tests): one test for whether the result meets expectations and multiple tests for checking the analysis. We then present a procedure to assess the quality of these unit tests based on their accuracy and redundancy on simulated versions of the original data. The accuracy is assessed using binary classification metrics, *i.e.*, precision and recall, while redundancy is calculated using mutual information. This procedure can be used to conduct a sensitivity analysis, compare different analysis plans, and to identify the optimal cutoff point for the unit tests."
cite-method: natbib
bibliography: references.bib
documentclass: jds
format:
  pdf:
   keep-tex: true
   toc: true
   notebook-links: false
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
editor_options: 
  chunk_output_type: console
---

@@

* *Check for TODOs*
- Literature review: Section *diagnosing unexpected outcomes in data analysis* 
- *Discussion* and *Conclusion*
- In Section *Application*: provide more context on the PM10-mortality study and add reference of the [0, 0.005] PM10 coefficient
- Roger's Orcid???

>>>>

---
title: "My wonderful paper"
abstract: "Unexpected results in data analysis can prompt researchers to examine data quality and analysis steps. While some researchers can typically diagnose issues effectively with a few checks, others may struggle to identify appropriate checks to diagnose the problem. [an example of check] These checks are often informal and difficult to trace and discuss in publications, resulting in others questioning the trustworthiness of the analysis. To address this, we formalize the informal checks into an *analysis plan* that encompasses the analysis steps and (the unit tests): one test for whether the result meets expectations and multiple tests for checking the analysis. We then present a procedure to assess the quality of these unit tests based on their accuracy and redundancy on simulated versions of the original data. The accuracy is assessed using binary classification metrics, *i.e.*, precision and recall, while redundancy is calculated using mutual information. This procedure can be used to conduct a sensitivity analysis, compare different analysis plans, and to identify the optimal cutoff point for the unit tests."
author:
  - name: "H. Sherry Zhang"
    affiliation: "University of Texas at Austin"
    email: "huize.zhang@austin.utexas.edu"
    attributes:
      corresponding: true
  - name: "Roger D. Peng"
    affiliation: "University of Texas at Austin"
    email: "roger.peng@austin.utexas.edu"
cite-method: natbib
bibliography: references.bib
format:
 tandf-pdf:
   keep-tex: true
   fontsize: 12pt
   linestretch: 2
   notebook-links: false
preamble: >
  \usepackage{amsfonts,amsmath,amssymb,amsthm}
editor_options: 
  chunk_output_type: console
---

@@

* *Check for TODOs*
- Literature review: Section *diagnosing unexpected outcomes in data analysis* 
- *Discussion* and *Conclusion*
- In Section *Application*: provide more context on the PM10-mortality study and add reference of the [0, 0.005] PM10 coefficient
